\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4in,top=0.4in,right=0.4in, bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}


\name{Po-Yu Chen} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+(886) 983-960-657 \\ \href{mailto:slimon0216@gmail.com}{slimon0216@gmail.com} \\ \href{https://github.com/slimon110}{GitHub}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

% \begin{rSection}{OBJECTIVE}

% Software Engineer with 2+ years of experience in XXX, seeking full-time XXX roles.
Looking for a software engineering internship opportunity where I can leverage my skills and passion in programming, computer systems, and machine learning to make a valuable contribution to the team.

% \end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION, Taipei, Taiwan
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

% {\bf National Taiwan University (NTU)} \\
% \itab{ \textit{M.S.} in  {\bf Electrical Engineering}, GPA: 4.20/4.30}  \hfill \textit{Sep. 2022 - Jun. 2024(Expected)} \\
% \itab{ \textit{B.B.A.} in {\bf International Business}, GPA: 3.82/4.30} \hfill \textit{Sep. 2017 - Jun. 2022} \\
% \itab{  \textit{B.B.A.} in  {\bf Information Management}, \textit{Dual Major}} \hfill \textit{Sep. 2017 - Jun. 2022} 
% \item \textbf{Relevant Coursework}: Data Structures,  Algorithms, Operating System, Computer Networks, Computer Architecture, Database Management, Machine Learning, Deep Learning for Computer Vision, Fault Tolerant Computing

{\bf National Taiwan University (NTU)}
\begin{itemize}
    % \itemsep -3pt
    \item \textit{M.S.} in {Electrical Engineering}, GPA: 4.20/4.30, Class Rank: 2/24  \hfill \textit{Sep. 2022 - Jun. 2024(Expected)}
    \item \textit{B.B.A.} in {International Business}, GPA: 3.82/4.30 \hfill \textit{Sep. 2017 - Jun. 2022}
    \item \textit{B.B.A.} in {Information Management}, \textit{Double Major} \hfill \textit{Sep. 2017 - Jun. 2022}
    \item {Relevant Coursework}: Data Structures,  Algorithms, Operating System, Computer Networks, Computer Architecture, Database Management, Machine Learning, Deep Learning for Computer Vision, Fault Tolerant Computing
\end{itemize}

\end{rSection}


% ----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------

\begin{rSection}{SKILLS}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
    Technical & Familiar: C/C++, Python, PyTorch, CMake, Git, Unix/Linux \\ 
                & Experienced: GNU toolchain, Docker, CUDA, Multi-thread/Heterogeneous/Parallel/Socket Programming \\ \\
    Language & Mandarin (Native), English (Intermediate), Japanese(Beginner)
    \end{tabular}\\
\end{rSection}



%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{WORK EXPERIENCE} 
\textbf{Awesome Research} \textit{- Crypto hedge fund startup formed by 15 undergraduates from NTU EE/CS} \hfill \textit{Jan 2022 - Sep 2022} \\  
\textit{Software Engineer and Quantitative Trader}  \hfill {Taipei, Taiwan} 
    \begin{itemize}
        % \itemsep -3pt {} 
        \item Led a 5-person team to design RESTful/WebSocket API and develop toolkit for crypto trading with the help of Boost C++ Libraries, C++ REST SDK and OpenSSL in test-driven development process
        \item Maintained projects with shell scripts, CMake, Git, and Conan
        \item Refactored codes and wrote cases to achieve loose coupling and high code coverage
        \item Analyzed and optimized codes using Google Benchmark, and debugged with GDB and sanitizer
        \item Implemented and deployed an automated arbitrage strategy independently using modern C++
    \end{itemize}




% \textbf{National Taiwan University} \hfill \textit{Sep 2021 - Jan 2022} \\
% \textit{Teaching Assistant, Programming for Business Computing, Prof. Ling-Chieh Kung} \hfill \textit{Taipei, Taiwan}
% \begin{itemize}
%     \item Checked and corrected the contents and test data of weekly homework before released
%     \item Held weekly office hour to answer questions for 100+ students
% \end{itemize}
    
\end{rSection} 


\begin{rSection}{PROJECTS}
\vspace{-1.25em}

% \item {\bf Matrix Multiplication Optimization for Graph Neural Network(GNN)} \hfill \textit{Feb. 2023 - Present}\\
% Integrated custom C++/CUDA functions into python as extensions through PyTorch C++/CUDA api.
\item {\bf Byzantine Distributed Optimization on Non-linear Constrained Problem} (\href{https://github.com/slimon110/2022_Fault_Tolerance/blob/master/FT-Report/FT-Report.pdf}{Paper Link})  \hfill \textit{Oct, 2022 - Jan, 2023}
\begin{itemize}
    \itemsep -3pt
    \item Implemented algorithms proposed by colleagues and conducted experiments independently to using python(SciPy)
\end{itemize}

% \item {\bf 3D Indoor Scene Long Tail Segmentation} \hfill \textit{Nov, 2022 -  Jan, 2023}
% \begin{itemize}
    % \item Read paper in ECCV 2020 and reproduce the result using the 
% \end{itemize}

\item \textbf{Trademark Retrieval Mobile App} (\href{https://play.google.com/store/apps/details?id=meow.logoshot&hl=zh_TW&gl=TW&pli=1}{Google Play}/\href{https://apps.apple.com/tw/app/logo-shot/id1611756574}{App Store}) \hfill \textit{Feb. 2021 - Jan. 2022}
\begin{itemize}
    \itemsep -3pt
    \item  Built a CNN-based model to learn representations from images for downstream image retrieval task.
\end{itemize}
% \end{itemize}

\item \textbf{Secure P2P Micro-payment System} \hfill \textit{Nov. 2021 - Jan. 2022} 
\begin{itemize}
    \itemsep -3pt
    \item Built client and multithreaded server, which communicated in CLI through secure TCP/SSL socket with C++, with all communications encrypted by OpenSSL toolkits.
    % \item Used a job queue and thread pool to enable the server to handle multiple connections in parallel, and used mutex, condition variable to guarantee thread-safety and non-busy waiting.
    % \item Leverage to enable the server to handle multiple connections in parallel, and used mutex, condition variable to guarantee thread-safety and non-busy waiting.
\end{itemize}

\item \textbf{Product Recommendation System for Fubon Financial Holding Co., Ltd.} \hfill \textit{Feb. 2021 - Jun. 2021}
\begin{itemize}
    \itemsep -3pt
    \item Built a recommendation system to assist the precision telemarketing, using ensemble and over-and-under-sampling techniques to achieve AUC score equally matched with the real inner system adopted by Fubon.
\end{itemize}

% \item \textbf{Taipei Pre-owned Housing Prices Prediction} \hfill \textit{Sep. 2020 - Jan. 2021} \\
% Built a price-prediction model to alleviate the price non-transparency problem in secondhand house market. Used Google Geocoding API to collect the distance from each house to nearest MRT station to enrich data and improve performance.

% \item \textbf{House price}
% \item \textbf{capstone}


\end{rSection} 

%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Curricular Activities} 
\textbf{National Taiwan University Guitar Club}, \textit{Education Officier} \hfill \textit{Sep. 2020 - Jun. 2021}
\begin{itemize}
    \item Held classes weekly and taught guitar in front of hundreds of club members
\end{itemize}

\textbf{Taipei Medical University 36th Guitar Competition}, \textit{Finalist}  \hfill \textit{Nov. 2019 - Dec. 2019} 


\textbf{National Taiwan University Orientation Camp}, \textit{Camp counselor}  \hfill \textit{Jun. 2019 - Aug. 2019} 


% \textbf{orientation camp}

\end{rSection}

%----------------------------------------------------------------------------------------



\end{document}
